\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-08-04 doc/sw-cfhtls.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps CFHTLS Results Paper
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

@@

\title[\sw]
{\SW: New Lens Candidates from the CFHT Legacy Survey}

@@

@@

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}

@@

\begin{abstract}

We present X new strong gravitational lens candidates found in the CFHT Legacy
survey by the \sw collaboration.

@@

In this paper, we ... try to answer the following questions:

\item ...

\item ...

\item ...

This paper is organised as follows. In \Sref{sec:sw} we give a brief overview
of the \sw system, focusing on the aspects most relevant to the interpretation
of the results of this first lens search. In \Sref{sec:data} we introduce the
CFHTLS imaging data. ... We discuss the implications of our results for future
lens searches in \Sref{sec:discuss} and draw conclusions in
\Sref{sec:conclude}.

@@

\section{\sw Overview}
\label{sec:sw}

@@

\section{Data}
\label{sec:data}

Definitions: training subjects and test subjects. Sims and duds.

@@

\subsection{The CFHT Legacy Survey}
\label{sec:data:CFHTLS}

Describe survey. Refs.

Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
comparison of techniques. Lenses not yet found by robots, detectable by
humans?

Blind search strategy.
Preparation of data: divide survey into overlapping tiles.

@@

\subsection{Image Presentation}
\label{sec:data:display}

Presentation of images. Uniform scales, to build intuition and avoid rescales
due to bright objects. Arcsinh stretch, to bring out low SB features. 
Approximately optimized, how? Examples of images.

\subsection{Known Lenses}
\label{sec:data:knownlenses}

@@

Completeness and purity with regard to known lenses.

\subsection{Stage 1 Classification}
\label{sec:results:stage1}

@@

\subsection{New Lens Candidates}
\label{sec:results:newlenses}

@@

Differences with robots: what types of lenses are found at \sw?

@@

@@

\section{Conclusions}
\label{sec:conclude}

Summary of CFHTLS project.

Crowd-sourced gravitational lens detection works, in terms of the
classification of the CFHTLS image dataset as described here, in the following
specific ways:

@@

\item Real (robotically-detected and expert-confirmed) lenses are
recovered/missed at similar/comparable/different rates to the
training set.

\item Completeness, purity of \sw sample to known lenses.

\item Partial test of supervised vs unsupervised learning, comment.

\item Which real lenses were missed? False negatives, what we conclude from
that.

\item We found a
sample of new gravitational lens candidates with the following properties: ...

\item An expert-graded sample of size N, divided among several types, compares
as follows.

\item The SW lenses are different from the robotically (RingFinder and
ArcFinder) detected lenses, in the following ways.

@@

Sum up, end.

@@

\input{acknowledgments.tex}

@@

% \appendix

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps II: CFHTLS 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[\sw II]
{\SW: II. Did we beat the lens finding robots in CFHTLS?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2013}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
We present X new strong gravitational lens candidates found in the CFHT
Legacy
survey by the \sw collaboration.

@@

{\it Describe various lens finding algorithms and the motivation for this
particular project with \cfhtls. Already searched by robots: enables comparison of techniques. Lenses not
yet found by robots, detectable by humans? }

In Paper I, we describe the \sw website, an online system that enables
crowd-sourced detection of gravitational lenses. In this paper, we
describe our first lens search with \sw in the \cfhtls data which we
refer to as Paper II.

This paper is organised as follows. In \Sref{sec:sw} we give a brief
overview of the \sw system, focusing on the aspects most relevant to the
interpretation of the results of this first lens search. In
\Sref{sec:data} we introduce the \cfhtls imaging data and the known lens
samples from the \cfhtls. In \Sref{sec:}, we explain the training sample
generated to aid the \sw users in the lens search. In
\Sref{sec:results}, we present the new lens candidates and our findings.
We discuss the implications of our results for future lens searches in
\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.

@@

\section{Data}
\label{sec:data}
\subsection{The CFHT Legacy Survey}
\label{sec:data:cfhtls}

The Canada-France-Hawaii Telescope Legacy Survey (CFHTLS) is a
photometric survey in five optical bands ($u^*g'r'i'z'$) carried out
with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
and a pixel size of 0.186\arcsec. The \cfhtls WIDE covers a total area
of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
W4. The field W1 has the largest sky coverage of 63.65~deg$^2$. The
fields W2 and W4 have similar sky coverages of 20.32~deg$^2$ and
20.02~deg$^2$, respectively\footnote{These numbers are estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.
The field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice
as large as W2 and W4.

The \cfhtls imaging is very homogeneous and has great image quality. Most of
the lensed arcs are much brighter in the $g$ band thus, deep imaging in
this band is desirable. The limiting magnitude is 25.47 for the $g$ band
which goes the deepest among all of the five bands. The mean seeing in
the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
magnitude for all bands is 30. These characteristics make \cfhtls ideal
to do visual inspection for finding lenses.  We use the data from the
final T0007 release taken from the Terapix
website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}}
for this work.

We note that the \cfhtls is a niche survey with a unique combination of
wide imaging with deep sensitivity. It is a precursor to the ongoing
wide imaging surveys such as the DES, KIDS and HSC and planned surveys
such as the LSST. Searching for lenses with \sw in the \cfhtls will
teach us important lessons and help prepare us for these larger imaging
surveys.

@@

\subsection{Known \cfhtls lens samples}
\label{sec:data:kls}

The \cfhtls data has been searched for lenses using semi-automated
algorithms, primarily, in the $g$ band which is optimal for finding
lenses. Here, we briefly mention the lens samples which were known to
the authors prior to the lens search with \sw.
The work
by \citet{Gavazzi2013} looks for bluish features around bright XXX
galaxies and has found XXX lens candidates at galaxy-scales.  The arc
finding lens search \citet{More2012} has found 127 lens candidates by
looking for arcs in $g$ band alone. This sample has both galaxy and
groups scale lens candidates. The \citet{Sygnet2009} is a search for
edge-on disk lenses done by selecting the galaxy's profile from the
Sextractor's output in the $i$~band and has 18 lens candidates.

For the purpose of transparency, the volunteers participating in
\sw-\cfhtls lens search were made aware of these known lens samples. Images
containing the lenses from these lens samples were labelled so in the
forum Talk where volunteers have the opportunity to discuss their
findings with other volunteers and the science team. XXX some references
to Paper I ?

\subsection{Image Presentation}
\label{sec:data:impres}
{\it Preparation of data: divide survey into overlapping tiles.

Presentation of images. Uniform scales, to build intuition and avoid rescales
due to bright objects. Arcsinh stretch, to bring out low SB features. 
Approximately optimized, how? Examples of images.}

We carry out a blind search over the \cfhtls fields where we, mainly, use
the g-r-i color information to look for signs of lensing. We extract
contiguous cutouts of size 81.84\arcsec\ (440 pixels). The neighbouring
cutouts have an overlapping region of 10\arcsec (54 pixels). If a
possible lens candidate is too close to the edge of a cutout, this
overlap allows the inspector to get a clearer view of the same candidate
in a neighbouring cutout. We note that since the images are shown
randomly, a given inspector may not necessarily come across the
neighbouring cutout unless the inspector classifies a lot of images.
However, this is not a problem since we our user base is extremely large
and we get multiple classifications of the same image.

\section{Training sample: Simulated lenses}
\label{sec:ts}

{\it State the importance}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/sim_cgq.pdf}
\caption{ \label{fig:sim}
Examples of the three types of simulated lenses.
}
\end{center}
\end{figure*}

\subsection{Methodology}
\label{sec:simmethod}

We create two main types of simulated lens sample a) galaxy-scale lenses and b)
group or cluster-scale lenses. The galaxy-scale lenses are further divided into two
types based on the nature of the background sources, namely, galaxies and
quasars. Below, we describe how each type of the lens sample was generated.

\subsubsection{Galaxy-scale lenses} 
\label{sect:gallens}

The $N_{\rm src}$ behind a lens is then calculated by doing the
following integral,

\be
\label{eqn:nsrc}
N_{\rm src} = N_{\rm src}(>L_s,z_s) \int_{z_l}^\infty \sigma_{\rm lens}(\sigma,z_l,z_s,q) D_s^2 (1+z_s)^2 \frac{\rm d\chi}{{\rm d}z_s}
{\rm d}z_s 
\ee

\be
\label{eqn:nlum}
 N_{\rm src}(>L_s,z_s)= \int_{L_{min}}^\infty \Phi(L_s,z_s) {\rm d}L_s
\ee

where $\Phi(L_s,z_s)$ is the source luminosity function per unit comoving
volume, $q$ is the projected axis ratio of the lens ellipticity, $\chi$ and
$D_s$ are the comoving and angular diameter distances to the source,

We use the elliptical galaxy (LRG) catalog from the \cfhtls XXX to select
all the foreground galaxies (e.g. $z<1$) that are potential lenses for the
simulated sample. We exclude all those galaxies whose positions match with the
lensing galaxies from the known \cfhtls~SL2S lens samples \cite{More2012}
within 2~arcsec (XXX check).

First, we calculate the luminosity and velocity dispersion of each potential
lensing galaxy using the CFHT Megacam $g$ and $r$ band magnitudes along with the
photometric redshift ($z_l$) from the LRG catalog.  The Megacam magnitudes are
converted to SDSS magnitudes\footnote{
    http://www3.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/megapipe/docs/filters.html} and
are further k-corrected to redshift $z=0.1$ \citep{Frei1994}. We assume that the
evolution of galaxy luminosities is similar to that determined by
\citep{Faber2007}, that is, a decline of $1.5$ in the $m_{r*}$ from redshift $z=1$
to $z=0$ (see Eq.~\ref{magstar}).

\be
\frac{L}{L_{*}}=10.0^{-0.4~(m_{r \rm SDSS}-m_{r*})} 
\ee

where $m_{r*}$ is
\be
\label{magstar}
m_{r*}=-20.44+ 1.5~(z_{l}-0.1) \,.
\ee

We use the $L-\sigma$ relation from
\citep{Parker2007} to get the velocity dispersion as given in Eq.~\ref{magstar2}.

\be
\label{magstar2}
\sigma=142 \left(\frac{L}{L_{*}}\right)^{1/3} 
\ee

Next, in order to decide whether a galaxy is likely to act as a strong lens, we
calculate the lens cross-section ($\sigma_{\rm lens}$) and the number of sources
($N_{\rm src}$) that are in the background. Following \citep{Keeton2000a}, the lens
cross-section is calculated analytically for an isothermal model and is given by

\be
\sigma_{\rm lens}=b_I^2 \, \int_0^{2\pi} 0.5 r^2(\theta) d\theta
\ee

where $b_I$ is 
\be
b_I = b_{\rm SIS} \epsilon_3/sin^{-1}(\epsilon_3) \,,
\ee

the eccentricity ($\epsilon_3$) is 
\be
\epsilon_3=(1-q_3^2)^{1/2}
\ee

and the projected axis ratio is given by
\be
q_k=\sqrt{q_3^2 {\rm sin}^2i_e+{\rm cos}^2i_e} \,.
\ee

In the above equations, $q_3$ is the 3d axis ratio of the ellipsoid and $i_e$ is
the inclination angle. Also, $b_{\rm SIS}= 4\pi
\frac{c^2}{\sigma^2}\frac{D_{s}}{D_{ls}D_l}$ and is referred to as the
Einstein radius where $D_s$,$D_l$ and $D_{ls}$ are angular diameter distances to
the source, the lens and between the lens and source, respectively.

%Comparing \citep{keeton00a} with \citep{kormann94} suggests that $b_I = sqrt(q)*b_{SIS}$

Next, if the foreground galaxy can act as a lens and has at least one source in the
background, then we determine a redshift ($z_s$) and $i$-band magnitude of the
background source(s). We assume two types of background sources namely, galaxies
and quasars. For each source, the redshift and magnitude are generated by drawing randomly from
the following redshift and luminosity distributions. For
galaxies, we assume the redshift distribution is

\be
\label{eqn:ps}
p_s=\frac{\beta z_s^2 {\rm exp}({\frac{z_s}{z_0(m_{\rm lim})}})^\beta}{\Gamma(3/\beta)z_0^3(m_{\rm lim})}
\ee

where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13m_{\rm lim} - 2.2$ and the
luminosity function is

\be
\label{eqn:ns}
n_s=\int^{m_{\rm lim}}_{-\infty} \frac{n_0 {\rm d}m}{\sqrt{10^{2a(m_1-m)}+10^{2b(m_1-m)}}}
\ee

with parameters $a=0.30$, $b=0.56$, $m_1=20$ and $n_0=3\times10^3~deg^{-2}$ as
given in \citep{Faure2009} and references therein. For quasars, we calculate
the luminosity function by following the prescription of \citep{Ogur2010} and
use k-corrections by \citep{Richards2006}.

%alp=-0.5;
%kcorr=-2.5*(1 + alp)*log10(1+zz);
%Dlum=cc.Dlofz(zz)/p.hval;
%DM=5*log10(Dlum);
%Mabs=mag-kcorr-DM-25.0;
The luminosity function is expressed as
\be
\frac{{\rm d}\Phi}{{\rm d}M}=\frac{\Phi_{*}}{10^{0.4(\alpha+1)(M_{\rm abs}-M_{*})} + 10^{0.4(\beta+1)(M_{\rm abs}-M_{*})} }
\ee

where the normalization, $\phi_{*}=5.34\times10^{-6} h^3$ Mpc$^{-3}$ and break
magnitude, $M_*=-20.90 + 5 {\rm log} h - 2.5 {\rm log} f(z)$. The redshift
dependent factor in $M_*$ is given by

\be
f(z)=\frac{e^{\zeta z_s}(1+e^{\xi z_*})}{(\sqrt{e^{\xi z_s}}+\sqrt{e^{\xi z_*}})^2} \,.
\ee
We adopt the best-fit values $\zeta=2.98$, $\xi=4.05$, $z_{*}=1.60$
\citep{Oguri2010}. For the faint end slope, we use $\beta=-1.45$ whereas for
the bright end slope, we use $\alpha=-3.31$ when $z_s<3$ and $\alpha=-2.58$ at
higher redshifts, as prescribed by \citep{Oguri2010}. 
respectively. We note that when calculating $N_{\rm src}$, the source
number density is artificially boosted by a factor (see Table~\ref{tab:thresh})
to increase the occurrence of simulated lenses. This helps in creating a large
enough sample to carry out various performance tests.

Next, we determine properties of the background source for every lens. We follow
similar procedures for both background galaxies and quasars. For simplicity, we
simulate a single background source behind every lens. In order to select one
background source from the $N_{\rm src}$ per lens, we do ray-tracing for all of the
$N_{\rm src}$ sources with {\sc gravlens} \citep{Keeton2000} and choose sources that
satisfy criteria as given below. We determine fluxes of the lensed images
and the total magnification of each of the lensed source. We draw a random
source for which the flux of the second brightest lensed image and the total
magnification of all lensed images are above the thresholds given in
Table~\ref{tab:thresh}.

Since we want to produce realistic looking lens systems, we simulate lenses in
each of the five \cfhtls~filters. The colors of the background galaxies are drawn
randomly from the photometric CFHTLenS catalog
\citep{Hildebrandt2012,Erben2013}.  Similarly, we use a quasar catalog from the
SDSS Data Release 9 \citep{Paris2012} from which colors are drawn to simulate
quasar lenses. Next, we assume deVaucoleur's profile to account for the size
and shape of the galaxies. The ellipticity and the position angle are drawn
randomly between the range given in Table~\ref{tab:thresh}. The effective
radius of the galaxy is estimated from the Luminosity$-$size relation
\citep{Bernardi2003} given by 
\be
R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2}
\ee
where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to follow a
Gaussian profile where the $\sigma$ is equated to that of the median seeing for
every filter. The median seeing values are taken from Table 4 of the official
Terapix T0007 release explanatory document \footnote{
    http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.

Once all the parameters are determined for the lens and source models, {\sc
gravlens} is used to simulate lensed images.  After accounting for the shot
noise in the lensed images and convolving them with the median seeing in each of
the filters, the simulated image is added to the real \cfhtls~image centered
on the lensing galaxy. Note that we ensure that the lensed galaxies and
lensed quasars do not have the same lensing galaxy in the foreground. Similarly,
the lensing galaxies from the galaxy-scale lenses are distinct from the central
galaxies of groups-scale lenses which are described in the following section.

\subsubsection{Groups-scale lenses}

At group or cluster-scales, the brightest group galaxy (BGG) at the center alone
does not cause strong lensing. We need to account for the extra convergence
arising from the dark matter component as well as satellite galaxies, at least,
in the inner regions which are typically responsible for the multiple lensed
images \citep{Oguri2005,Oguri2006}. Owing to the lack of an appropriate group
catalog for our purposes, we create a basic group catalog based on the
magnitudes and photometric redshifts available for the \cfhtls. We select all
galaxies with 10$^{10.8} M_\odot$ as the BGGs. We select the member galaxies
such that their photometric redshifts are within $\delta z = 0.01$ of the BGG
and within an aperture of $250$~Kpc.

We adopt an isothermal ellipsoid for the BGG and members whenever the
ellipticities are available else we use an isothermal sphere. On the other hand, we
adopt an NFW profile for the underlying dark matter halo. Assuming a constant
mass-to-light ratio of $3 \times 0.7$~h~$M_{*}/L_{*}$, we use the BGG luminosity
to estimate the stellar mass. The stellar mass$-$halo mass relation
\citep{behroozi13}, including random scatter, is then used to calculate the halo
mass for the lens. Given the halo mass, other key parameters such as the scale
radius ($r_s$) and the density at the scale radius ($\rho_s$) can be determined for an
NFW profile.

As described in Section~\ref{sect:gallens}, we calculate the luminosity and
velocity dispersion for the BGG and each of the member galaxies. Next, we
calculate the lens cross-section for each potential lensing group. The
complexity in the lens models makes it analytically intractable to calculate the
size of the caustics\footnote{The lens mass distribution determines size and
shape of the caustics. Any source located within the caustics will form multiple
lensed images which is the criteria for strong lensing. To further
understand caustics, see XXX.}.  Hence, we use {\sc
gravlens} to determine the area covered by the caustics. We consider only
galaxies as our background source population since group or cluster-scale quasar
lenses are not expected to be found in the \cfhtls (check XXX).  Following the same
procedure as described in Section~\ref{sect:gallens}, we calculate the number of
galaxies expected to lie behind every potential lensing group (see
Eq.~\ref{eqn:nsrc}). As before, for each background galaxy within the lens cross-section, a
redshift and an $i$-band magnitude is determined by drawing galaxies randomly
from the respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).

All those groups that are found to have no background galaxies within the
cross-sectional area are rejected and the rest are included as potential lenses.
As mentioned earlier, we artificially boost the total number of sources behind
every lens but ensure that (check XXX) the statistical properties such as the profile of the
image separation distribution are not affected (see \Fref{fig:remudist}). We
follow the same procedure and apply the same thresholds to determine properties
of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
in the previous section. The simulated images are added to the real \cfhtls~images
with the BGGs as the center.

@@

\subsection{Simulated Lens Sample and Catalog Description}

\begin{table}
\begin{center}
\caption{ \label{tab:thresh} 
Thresholds used in the selection of the simulated lenses. }
\begin{tabular}{l l l l l}
\hline
Name  &  \multicolumn{2}{c} {gal}  & \multicolumn{2}{c}{qso} \\ 
      & min  &  max  & min & max \\
\hline
\hline
Source Redshift  & 1.0 & 4.0  & 1.0  & 5.9 \\
Source Magnitude & 21.0 & 25.5 & 21.0 & 25.5 \\

boost factor & 100 (40$\dagger$)  &  & 1200 & \\

Second brightest image & 23  & & 23 & \\
Total magnification & 19 & & 20 & \\

Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
Lens shear pa &  0 & 180 & 0 & 180  \\
Source ellipticity & 0.1 & 0.6 & & \\
Source PA & 0 & 180 & & \\
\hline
\end{tabular}
{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
\end{center}
\end{table}

In this section, we describe some of the properties of our simulated sample for
each of the three types of lens samples.

The \Fref{fig:remudist} shows Einstein radius distribution for the
galaxy-scale (dashed for background quasars and dotted for background galaxies)
and groups-scale simulated lenses. For comparison, we show the expected
distributions (blue dashed-dotted curves) for an SIS-like density profile at
galaxy-scales and an NFW+Hernquist profile at groups-scales. The 
theoretical curves are taken from \citep{More2012} wherein the models are
explained in detail. We note that the model we adopt at groups-scale also
includes SIS or SIE components for the group members unlike the theoretical
prediction. The theoretical curves have arbitrary normalizations.

We show the redshift and magnitude distributions of the lensing galaxies in the
left and right panels of \Fref{fig:lensprop}
respectively. Furthermore, we overplot the distributions of respective
properties of the SARCS lenses from \citep{More2012} for comparison with arbitrary
normalizations. We note qualitative similarities between the simulated and the
real lens samples.

Similarly, we show the ellipticity and the position angle of the simulated lens
galaxy population extracted from the T0007 release of the \cfhtls~catalogs in the
left and right panels of \Fref{fig:lensprop}, respectively. As before, the
dashed-dotted (blue) curves show the same distribution for the SARCS lens
population with arbitrary normalization \citep{More2012}.

%We show the source redshift and magnitude distributions for each of the three
%lens samples in the left and right panels of \Fref{fig:szmdist},
%respectively. The peak of the source redshift distribution both for the galaxies
%and quasars is known to be between $2<z<3$ from various lens samples (add
%references XXX). This consistent with our simulated sample as expected. The
%magnitude distribution of the simulated sample, on the other hand, is
%specifically tailored to the requirements of \sw.  The goal was to generate a
%lens sample that has a fair balance of both bright and faint lensed images since
%the training sample should neither be too easy nor too difficult for the citizen
%scientists.

We produce catalogs with lens and source properties for each of the three types
of lenses. These catalogs are available XXX. The catalogs typically have lens
position, redshift, magnitudes, Einstein radius, ellipticity (whenever
available) and shear (for galaxy-scale lenses only). For the background
sources, we provide the offset from the lens center, redshift, magnitudes,
total magnification, number of lensed images. Additionally, ellipticity and
effective radius when the background sources are galaxies.

%magdiff=5*0.1;
%zdiffq=0.1;
\begin{figure*}
\begin{center}
\includegraphics[scale=0.85]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS XXXX check? 
}
\end{center}
\end{figure*}

%\begin{figure*}
%\begin{center}
%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_srczmag.eps}
%\caption{ \label{fig:szmdist}
%Redshift distribution on the left and magnitude distribution on the right of the
%simulated sample for the background sources. The different types of lines show the
%distribution correspond to the three types of simulated lenses galaxy-quasar,
%galaxy-galaxy and group-galaxy. 
%}
%\end{center}
%\end{figure*}
%
%
%\begin{figure}
%\begin{center}
%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_reff.eps}
%\caption{ \label{fig:reffdist}
%Distributions of magnification (left) and source effective radius in units of
%pixel (right).
%}
%\end{center}
%\end{figure}

@@

\section{Training sample: Duds and False positives}
\label{sec:dfp}

A good training sample consists of a representative set of objects that
one wants to find and another set of objects which appear to be from the
former set but are of different origin in reality and which one can
learn to discard efficiently. Indeed, we wanted to have a good training
sample for the \sw users so that they can correctly identify the true
lens candidates. Hence, in addition to the simulated lenses, we
added a sample of duds and false positives to the training sample. Duds
are images which have been visually inspected by experts and confirmed
to contain no lenses.  False positives are systems which look like
lenses but are not, for example, spiral galaxies, starforming galaxies,
chance alignments of features arranged in a lensing configuration and
stars.

We selected a sample of 450 duds for the Stage I classification in \sw
(see XXX) and a sample of XXX false positives for the Stage II
inspection (see XXX). The sample of false positives was selected from
the candidates which passed the Stage I of \sw. We note that this is the
first time, we have a systematically compiled sample of visually
inspected false positives by the \sw users and categorized by the
science team. Such a sample is tremendously helpful for training and
understanding performances of various lens finding algorithms (refer
james, sherry's paper ? XXX)
{\bf TBA data products; make the FP sample available}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Recovery of lenses}
\label{sec:results:reco}

{\it Describe which lenses were recovered and explain any cases missed by
citizen scientists}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
%
%\begin{longtable*}{l c c c c c c c l}
%\caption{ \label{tab:all} 
%Characteristics of lens candidates from the \SA sample. }\\
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endfirsthead
%
%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
%\endhead
%
%\hline  
%\multicolumn{11}{p{15cm}}{
%{\bfseries
%{\bf m:} This galaxy falls within the masked region as per the catalog from
%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
%and/or redshift are not from the catalog instead are measured by the author.
%}  }\\
%
%\endlastfoot
%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
%\end{longtable*}
%
\subsection{Stage 1 Classification}
\label{sec:results:stage1}

@@

\subsection{Discovery of lenses}
\label{sec:results:disc}

{\it Describe the newly found lenses and explain for a few
cases why they were missed }

\subsection{\cfhtls completeness and purity}
\label{sec:results:sample}

{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
as function of probability P.

Summarize performance at some fiducial threshold: eg P = 95\%.}

@@

{\it Differences with robots: what types of lenses are found at \sw?

@@

Describe the importance of this kind of study 
- being able to quantify the completeness of the lens samples
- state how this will be used in a future \sw paper }

We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. We do not find any obvious dependency in the rate of
detections as a function of the position of a given lens for both
simulated and real lens sample. Thus, the completeness of the lens
sample is not affected by whether a lens is located close to the border
or well within the center (see  Figure~\ref{fig:comppos}).  {\bf TBD: redo the completeness vs posn
figure using the final real lens sample}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
\caption{ \label{fig:comppos}
Completeness as a function of location of lenses. Simulated (left) and
real lens (right) samples are shown. {\bf: TBD - Add a third color for
P$>$ Pthresh which will be defn of "accepted"} Irrespective of whether the
lenses are detected or rejected and whether they are simulated or real,
there is no obvious dependency on where the lenses are located. 
}
\end{center}
\end{figure*}

\subsection{Limitations and Caveats of the training sample}
The simulated sample has certain limitations due to lack of our understanding of
various phenonmena in the Universe and due to uncertainties in various
parameters of our model. Here, we describe some of the cases or aspects in which the
simulations are known to have failed or seem unrealistic.

The parameters required by various scaling relations and the models primarily
depend on the photometry of the galaxies, groups and quasars detected in the
survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
which are fainter have poor photometric measurements. This causes relatively
larger uncertainties in its luminosity and velocity dispersion and leads to
simulated lenses which look implausible. For example, due to a larger
uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
may have larger image separation than what is expected given the visual priors
from the galaxy.

At group-scales, the photometric and redshift estimates are used when
defining the group membership. Therefore, errors in redshift estimates generate
galaxy groups with BGG or member galaxies with dissimilar properties. In some
cases, low redshift spiral galaxies are incorrectly assigned high redshift.
Spiral galaxies are typically less massive and low redshift spiral galaxies are
unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
are not convincing.

We use single Sersic component to describe the light profiles of background
galaxies. This is clearly not the most accurate description for galaxies,
especially, star-forming galaxies which form a significant fraction of the
lensed galaxy population. Star-forming galaxies have complex structures such as
star forming knots, spiral arms, bars and disks.

@@

\section{Summary and Conclusions}
\label{sec:conclude}
In this paper, we describe the framework and procedure used to generate
simulated lens sample for the blind lens search in the \cfhtls survey in
collaboration with \sw. The aim of this lens search is to find lenses that have
been missed by lens finding algorithms. The simulated lens sample is used for
training the citizen scientists, calibrating their performance and rejecting
unlikely lenses from the sample based on the classifications of citizen
scientists. As a result, the simulated lenses need to consist of realistic
looking lenses.

We use the photometric and redshift catalogues for the foreground galaxies and
additionally, color catalogues for background galaxies and quasars. We
use scaling relations to relate light properties to properties such as mass and
size to generate lens models. We further account for the
instrumental effects such as seeing and noise before creating the final lensed
images of model background sources. We add the lensed images on top of the real
galaxies and groups in the \cfhtls data in all filters.

We draw the following conclusions:

@@

\item Crowd-sourced gravitational lens detection works, as shown in by comparing with real lenses in CFHTLS:
Real (robotically-detected and expert-confirmed) lenses are
recovered/missed at similar/comparable/different rates C’\% and P’\% - this is a partial test of supervised vs unsupervised learning

%Which real lenses were missed? False negatives

\item We found a sample of new gravitational lens candidates. An expert-graded sample of size N, divided among several types.
The SW lenses are different from the robotically (RingFinder and ArcFinder) detected lenses, in the following ways.

% An expert-graded sample of size N, divided among several types.

@@

@@

\input{acknowledgments.tex}
This work is based on observations obtained with MegaPrime/MegaCam, a joint
project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
is operated by the National Research Council (NRC) of Canada, the Institut
National des Sciences de l'Univers of the Centre National de la Recherche
Scientifique (CNRS) of France, and the University of Hawaii. This research used
the facilities of the Canadian Astronomy Data Centre operated by the National
Research Council of Canada with the support of the Canadian Space Agency.
CFHTLenS data processing was made possible thanks to significant computing
support from the NSERC Research Tools and Instruments grant program.
This work was supported by World Premier International Research Center
Initiative (WPI Initiative), MEXT, Japan.

@@

\appendix

@@

\bibliographystyle{apj}
\bibliography{references_cfhtls}
%\bibliography{references}
